% Preamble
\documentclass[a4paper]{scrartcl}
\usepackage{latexsym}
\usepackage[nomarginpar]{geometry}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{microtype}
\usepackage{multirow}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\usepackage{times}
\usepackage[fontsize=12bp]{fontsize}
\usepackage{ragged2e} % for \justifying

% Page setup
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\parindent}{0pt}

\geometry{
    a4paper,
    lmargin=.8in,
    rmargin=.8in,
    tmargin=.8in,
    bmargin=.8in,
}

\renewcommand{\headrulewidth}{0pt}

\urlstyle{rm}

\begin{document}

\begin{center}
    \Large\textbf{Nikilesh Anusha N} \\
    \vspace{0.1em}
    \large{MA in General Economics $|$ \href{mailto:nikilnatesh@gmail.com}{nikilnatesh@gmail.com} $|$ +91-9442930141}
\end{center}

\vspace{1em}

June 25, 2025 \\

\vspace{1em}

Social Networks Lab Recruiting Team \\
J-PAL South Asia at the IFMR \\
Bangalore, India \\

\vspace{1em}

Dear Recruiting Team,

\vspace{0.5em}

\justifying

I am writing to express my sincere interest in the Research Associate position within the Social Networks suite at J-PAL South Asia. 
The opportunity to contribute to cutting-edge development research, particularly on the crucial role of social networks, deeply resonates with my professional trajectory and research interests. 
I am eager to learn more about core areas within this suite, such as social learning, information diffusion, network structure, and informal institutions, and to develop a deeper understanding of how these dynamics shape outcomes in developing economies. 
The prospect of contributing to and learning from the work of esteemed researchers like Professor Arun Chandrasekhar and Professor Emily Breza, whose research significantly shapes this field, is a primary motivator for my application.

My experience over the past year on the "Adaptation to Floods" study has provided a solid foundation in the practical aspects of research implementation and data management. 
I managed survey design, fieldwork oversight, and data cleaning using Stata and R, consistently aiming for reproducible, high-quality outputs. 
More recently, my role expanded to encompass data infrastructure development, including creating ETL pipelines for API-driven data integration. 
This has given me a comprehensive view of data management—from source integration to final analysis. Both my primary research and data analytics experience sparked my interest in network dynamics. 
For instance, observing the clustering of adaptation practices in villages prompted questions about information flow, while identifying key "vectors" within government departments during data capability assessments highlighted the importance of influential players in governance. 
These observations have further motivated me to pursue a deeper understanding of network structures and their impact.

Beyond data analysis, successfully navigating the practicalities of fieldwork has been equally critical to my professional development, honing my resilience and meticulousness. 
For example, when my field team encountered challenges with local villagers, I proactively engaged authorities and community leaders to ensure team safety and data collection continuity. 
Such experiences have reinforced the importance of adaptability, careful stakeholder communication, and meticulous attention to detail for maintaining research integrity in dynamic environments. 
I look forward to applying and refining these skills within the suite’s structured approach to high-stakes field experimentation.

My primary motivation is to channel my skills into this focused research area to gain and apply in-depth knowledge in experimental design and social network analysis. I am deeply committed to learning, contributing diligently, and supporting the suite's vital research.

My resume is attached for your review. I would immensely appreciate the opportunity to further discuss how my background and interests align with the position. Thank you for your time and consideration. I look forward to the possibility of speaking with you.
\vspace{1.5em}
\\
Sincerely, \\
Nikilesh Anusha N

\end{document}