% Preamble
\documentclass[a4paper]{scrartcl}
\usepackage{latexsym}
\usepackage[nomarginpar]{geometry}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{microtype}
\usepackage{multirow}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\usepackage{times}
\usepackage[fontsize=10.5bp]{fontsize}

% Page setup
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\geometry{
    a4paper,
    lmargin=0.45in,
    rmargin=0.45in,
    tmargin=0.45in,
    bmargin=0.45in,
}

% Content formatting
\urlstyle{rm}
\raggedbottom
\raggedright

% Table formatting
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-6pt}\bfseries\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom Commands -------------------
\newcommand{\resumeSectionListStart}{\begin{itemize}[leftmargin=0pt, label = {}, itemsep=6pt, topsep=2pt]}
\newcommand{\resumeSectionListEnd}{\end{itemize}\vspace{-0.7em}}

\newcommand{\resumeSectionList}[5]{
    \item
    \makebox[\textwidth]{
        \begin{minipage}{0.993\textwidth}
            \begin{tabularx}{\textwidth}{Xr}
                \textbf{#1} & #2 \\
                #3 & \textls[-30]{#4} \\
            \end{tabularx}
            \vspace{-1pt}
            #5
        \end{minipage}
    }
    \vspace{-6pt}
}

\renewcommand{\labelitemii}{\textbullet}

% Section List - Description List
\newcommand{\sectionListDescriptionStart}{\vspace{-5pt}\begin{itemize}[leftmargin=0.35cm, itemsep=-3pt, topsep=0.2em]}
\newcommand{\sectionListDescriptionEnd}{\end{itemize}}

\newcommand{\sectionListDescription}[1]{
    \item \textls[-10]{\small#1}
}

% Document -----------------------
\begin{document}

% Heading and contact details ---------
\begin{tabularx}{\textwidth}{Xr}
    \textbf{{\LARGE Nikilesh Anusha N}} & \href{mailto:nikilnatesh@gmail.com}{nikilnatesh@gmail.com} $|$ +91-9442930141 \\
    Master of Arts in General Economics (2023) & \\
    \multicolumn{2}{l}{\parbox{\textwidth}{{\href{https://drive.google.com/drive/folders/1StHUmaa_8Rl1F6QX4WnqLDe8kx4IFtfE?usp=share_link}{\textcolor{MidnightBlue}{Writing Portfolio: Academic Research Sample (Google Drive Folder)}}}}}\\
\end{tabularx}\vspace{-3pt}

% Education ------------
\section{Education}
\resumeSectionListStart
    \resumeSectionList
        {Madras School of Economics}{Chennai, India}
        {Master of Arts - General Economics;   CGPA: 7.67 / 10}{August 2021 - May 2023}
        {\raggedright\textls[-40]{\small\itshape\textbf{Relevant Coursework:} Dissertation, Development Economics, Applied Microeconometrics, Environment \& Health, Industrial Org, Games \& Information}}
    \resumeSectionList
        {Christ (Deemed to be University)}{Bangalore, India}
        {Bachelor of Arts (Honors) Economics;  CGPA: 3.86 / 4}{June 2018 - May 2021}
        {\raggedright\textls[-40]{\small\itshape\textbf{Relevant Coursework:} Dissertation, Microeconomics, Research Methodoloy, Fundamentals of Growth \& Development, Advanced Econometrics, Behavioral Economics,  Public Economics, Computer Applications for Economics, Environmental Economics}}
\resumeSectionListEnd

% Experience ------------
\section{Research Experience}
\resumeSectionListStart
    \resumeSectionList
        {Data, Policy and Innovation Centre {\footnotesize\normalfont\textls[-20]{(A University of Chicago and Gov. of Odisha Partnership)}}}{Bhubaneshwar, India}
        {\itshape Research Associate}{February 2024 - Present}
        {
            \sectionListDescriptionStart
                \sectionListDescription{Managed end-to-end research for 2000-household flood adaptation study: survey design, fieldwork, data cleaning, descriptive analysis, mapping, and stakeholder reporting.}
                \sectionListDescription{Developed ETL data pipelines for government datasets (Gramodaya, SPDP, Health Assurance) including API extraction and DB setup, producing reproducible analytics.}
                \sectionListDescription{Spearheaded department-wide (13 line departments) data capability assessment impacting policy on departmental data officer appointments; co-led a high-impact workshop on effective data use principles.}
                \sectionListDescription{Presented critical data-driven findings and strategic recommendations to senior government officials (State Development Commissioner, Principal Secretary), shaping departmental data modernization efforts.}
            \sectionListDescriptionEnd
        }
    \resumeSectionList
        {The Energy and Resources Institute}{New Delhi, India}
        {\itshape Project Associate, Centre for Resource Efficiency and Governance}{23\textsuperscript{rd} August, 2023 -- 31\textsuperscript{st} January, 2024}
        {
            \sectionListDescriptionStart
                \sectionListDescription{Contributed to research on alternate livelihood opportunity for informal coal mining workers and ecosystem service valuation of high-altitude wetlands in Uttarakhand and Ladakh.}
                \sectionListDescription{Led literature review, survey instrument design, fieldwork, analytical framework review, and data analysis; collaborated on drafting and presenting the final technical report.}
            \sectionListDescriptionEnd
        }
    \resumeSectionList
        {Indian Institute of Management, Indore}{Remote}
        {\itshape Research Intern, Under the Mentorship of Dr. Sneha Thapliyal}{23\textsuperscript{rd} April, 2020 -- 8\textsuperscript{th} June, 2020}
        {
            \vspace{1pt}
            {\hspace*{-0.1cm}\small\textls[-20]{\textbf{Project:} Environment Regulation and Public Choice: A Study into the National Green Tribunal (NGT)}\vspace{0.4em}}
            \sectionListDescriptionStart
                \sectionListDescription{Assisted with data collection and conducted literature review of regulatory choice models related to environmental justice.}
                \sectionListDescription{Unique contribution by creating a Database with essential information summarizing the judgements of the NGT for the years 2018-2020.}
            \sectionListDescriptionEnd
        }
    \resumeSectionList
        {Centre for Economics and Social Studies, Hyderabad}{Remote}
        {\itshape Research Intern, Under the Mentorship of Dr. Vidya CT}{28\textsuperscript{th} March, 2020 -- 15\textsuperscript{th} May, 2020}
        {   
            \vspace{1pt}
            {\hspace*{-0.1cm}\small\textls[-20]{\textbf{Project:} Linking SMEs into Global Value Chains with special emphasis on Textile Industries}\vspace{0.4em}}
            \sectionListDescriptionStart
                \sectionListDescription{Conducted literature review and collected primary data through one-on-one interviews with SME stakeholders in the textile sector.}
                \sectionListDescription{Identified critical research gaps that contributed to refining the primary research question and study design.}
            \sectionListDescriptionEnd
        }
\resumeSectionListEnd

% Independent Research ------------
\section{Independent Research Projects}
\resumeSectionListStart
    \resumeSectionList
        {Energy Decomposition, Decoupling and Spatial Heterogeneity: A Study from the Indian Manufacturing Sector}
        {} %empty  stub
        {\textit{Masters Thesis $|$ Invited Paper Presenter at the 11th National Seminar on Industrial Statistics, 2023}}
        {} %empty stub
        {   
            \sectionListDescriptionStart
                \sectionListDescription{Investigated energy-growth decoupling hypothesis in India’s manufacturing sector using spatial, index, and causal decomposition analyses.}
                \sectionListDescription{Extended a two-factor energy decomposition model to a five-factor IQAT framework, adapting the IPAT model for sectoral energy analysis.}
            \sectionListDescriptionEnd
        }
    \resumeSectionList
        {An Empirical Inquiry into the Distortionary Effect of Bank Bailout Policies in India}
        {} %empty stub
        {\textit{Co-authored with Sriram S $|$ Presented at YERC'21, Meghnad Desai Academy of Economics $|$ Best Paper Award}}
        {} %empty stub
        {
            \sectionListDescriptionStart
                \sectionListDescription{Investigated moral hazard in India’s banking sector using a two-stage game-theoretic framework and regression analysis.}
            \sectionListDescriptionEnd
        }
    \resumeSectionList
        {The Role of Bank Heterogeneity and Market Competition in Monetary Policy Transmission Mechanism}
        {} %empty stub
        {\textit{Undergraduate Thesis, 2021}}
        {} %empty stub
        {
            \sectionListDescriptionStart
                \sectionListDescription{Examined the impact of bank heterogeneity, market competition, and bank-specific factors on monetary policy transmission using dynamic panel regression with data from 69 Indian banks.}
            \sectionListDescriptionEnd
        }
\resumeSectionListEnd

% Skills Summary ------------
\section{Skills Summary}
\vspace{-2pt}
\begin{itemize}[leftmargin=0pt, label = {}]
    \item
        \begin{tabularx}{\textwidth}{p{3cm}X}
            \multirow{2}{=}{\textbf{Programming}} 
            & \textbf{Proficient:} R, Stata, LaTeX, SurveyCTO, Git/GitHub \\
            & \textbf{Beginner: } Python \\
        \end{tabularx}
    \item 
        \vspace{-5pt}
        \begin{tabularx}{\textwidth}{p{3cm}X}
            \textbf{Languages}& \textbf{Proficient:} English, Tamil, Hindi\\
        \end{tabularx}
\end{itemize}

\end{document}